The \dealii Library, Version 9.2

### 2020-05-26 9.2/paper.tex
Add experiment for setup times

\pgfplotsset{compat=1.9}

@@

By replacing the collective communications during set up and removing the arrays
that contain information for each process (enabled by the application of consensus
algorithms and other modifications---a full list of modifications leading to this
improvement can be found online), we were able to significantly
improve the set up
time for large-scale simulations and to solve a Poisson problem with multigrid
with \num{12e12} unknowns.
\todo[inline]{Where did we solve for 12T unknowns? The largest I [Martin] have done is 2.1T unknowns.}
Figure~\ref{...} {\color{red}Update reference} compares the timings of a simulation (including set up) with the
previous release 9.1 and with the current release 9.2.
{\color{red}TODO[Peter/Martin] description of the results}

>>>>

\pgfplotsset{compat=1.9}
\definecolor{gnuplot@lightblue}{RGB}{87,181,232}
\definecolor{gnuplot@green}{RGB}{0,158,115}
\definecolor{gnuplot@purple}{RGB}{148,0,212}

@@

By replacing the collective communications during set up and removing the arrays
that contain information for each process (enabled by the application of consensus
algorithms and other modifications---a full list of modifications leading to this
improvement can be found online), we were able to significantly
improve the set up
time for large-scale simulations and to solve a Poisson problem with multigrid
with \num{2.1e12} unknowns.
Figure~\ref{fig:init_costs} compares the timings of simulations of various problem
sizes (including set up) on 49,152 MPI ranks using a matrix-free solver according
to~\cite{KronbichlerKormann2019,KronbichlerWall2018} discontinuous elements of
degree $5$ in a geometric multigrid (GMG) scheme with the previous release 9.1
and with the current release 9.2. While the times for the V-cycle have shown
excellent scaling before, many initialization routines have been considerably
improved, especially the enumeration of unknowns on the multigrid levels and
the setup of the multigrid transfer.

\pgfplotstableread{
dofs  grid  distdofs  mfsetup  mgtransfer  smoother  vcycle
14155776  0.347457  0.02424084  0.03346427  0.0105426  0.0108817  0.0035033
28311552  0.35134  0.0215024  0.0340963  0.0095201  0.010616  0.0035887
56623104  0.41577  0.0243593  0.0432297  0.011557  0.011667  0.0041244
113246208  0.42172  0.0323919  0.0427806  0.012983  0.011834  0.0043853
226492416  0.43565  0.0404079  0.0421606  0.012867  0.017305  0.0056340
452984832  0.5055  0.0500101  0.0562977  0.017739  0.022763  0.0061992
905969664  0.54552  0.065865  0.0641994  0.019445  0.037431  0.0087932
1811939328  0.5672  0.104909  0.080807  0.025395  0.063548  0.0133252
3623878656  0.65541  0.165071  0.129717  0.042294  0.12644  0.0218619
7247757312  0.74521  0.251417  0.221072  0.073314  0.21807  0.0339264
14495514624  0.84789  0.403463  0.36894  0.11425  0.4091  0.0669798
28991029248  0.91983  0.52435  0.5363  0.14189  0.79178  0.1322448
57982058496  1.0339  0.87448  0.93134  0.23863  1.5896  0.2539445
115964116992  1.2667  1.46016  1.70806  0.44101  3.1409  0.4956625
231928233984  1.7597  2.58121  3.3741  0.77624  6.2628  0.9857200
}\tableinit

\pgfplotstableread{
dofs  grid  distdofs  mfsetup  mgtransfer  smoother  vcycle
14155776  2.0148  0.9086  0.433886  1.3099  0.010685  0.0035033
28311552  1.8746  0.91078  0.576777  1.3093  0.010752  0.0035887
56623104  2.0924  0.98058  0.574183  1.4459  0.011831  0.0041244
113246208  2.3788  1.22025  0.547492  1.7919  0.011979  0.0043853
226492416  2.1254  1.50329  0.839219  1.7832  0.017819  0.0056340
452984832  2.4325  2.10171  0.711708  2.0263  0.023393  0.0061992
905969664  3.8911  3.58355  1.08478  2.5844  0.045697  0.0087932
1811939328  4.1803  4.379  0.784804  1.8947  0.061552  0.0133252
3623878656  2.6654  5.6073  0.833896  1.8912  0.1188  0.0218619
7247757312  2.7422  7.8463  0.741733  1.8477  0.21291  0.0339264
14495514624  2.765  9.9848  0.99218  1.8248  0.40665  0.0669798
28991029248  3.2901  15.0526  1.5124  2.6723  0.81013  0.1322448
57982058496  3.1927  21.0562  1.72831  2.1998  1.5905  0.2539445
115964116992  4.1485  31.0087  2.67998  2.9091  3.2009  0.4956625
231928233984  4.1787  47.195  4.2821  3.9558  6.3362  0.9857200
}\tableinitold

\begin{figure}
  \begin{tikzpicture}
    \begin{loglogaxis}[
      width=0.51\textwidth,
      height=0.38\textwidth,
          xlabel={\# DoFs},
          ylabel={time [s]},
          title={9.1 release},
          xtick={1.4e7,5.7e7,2.3e8,9.1e8,3.6e9,1.4e10,5.8e10,2.3e11},
          xticklabels={1.4$\times 10^7$,5.7$\times 10^7$,2.3$\times 10^8$,9.1$\times 10^8$,3.6$\times 10^9$,1.4$\times 10^{10}$,5.8$\times 10^{10}$,2.3$\times 10^{11}$},
          tick label style={font=\scriptsize},
          xticklabel style={rotate=25,anchor=north east},
          label style={font=\scriptsize},
          legend style={font=\scriptsize},
          %legend to name=legend:scalingMG,
          %legend cell align=left,
          %legend columns = 3,
          ymin=2e-3,ymax=8e1,
          grid, thick]
          \addplot table[x index = 0, y index={1}] {\tableinitold};
          \addplot[red,mark=square*] table[x index = 0, y index={2}] {\tableinitold};
          \addplot[gnuplot@green,mark=otimes] table[x index = 0, y index={3}] {\tableinitold};
          \addplot[gnuplot@lightblue,mark=triangle] table[x index = 0, y index={4}] {\tableinitold};
          \addplot[gnuplot@purple,mark=diamond] table[x index = 0, y index={5}] {\tableinitold};
          \addplot[black,mark=x] table[x index = 0, y index={6}] {\tableinitold};
    \end{loglogaxis}
  \end{tikzpicture}
  \hfill
  \begin{tikzpicture}
    \begin{loglogaxis}[
      width=0.51\textwidth,
      height=0.38\textwidth,
          xlabel={\# DoFs},
          ylabel={time [s]},
          title={9.2 release},
          xtick={1.4e7,5.7e7,2.3e8,9.1e8,3.6e9,1.4e10,5.8e10,2.3e11},
          xticklabels={1.4$\times 10^7$,5.7$\times 10^7$,2.3$\times 10^8$,9.1$\times 10^8$,3.6$\times 10^9$,1.4$\times 10^{10}$,5.8$\times 10^{10}$,2.3$\times 10^{11}$},
          tick label style={font=\scriptsize},
          xticklabel style={rotate=25,anchor=north east}, thick,
          label style={font=\scriptsize},
          legend style={font=\scriptsize},
          legend to name=legend:init,
          legend cell align=left,
          legend columns = 6,
          ymin=2e-3,ymax=8e1,
          grid]
          \addplot table[x index = 0, y index={1}] {\tableinit};
          \addlegendentry{create mesh};
          \addplot[red,mark=square*] table[x index = 0, y index={2}] {\tableinit};
          \addlegendentry{enumerate (mg) dofs};
          \addplot[gnuplot@green,mark=otimes] table[x index = 0, y index={3}] {\tableinit};
          \addlegendentry{init matrix-free};
          \addplot[gnuplot@lightblue,mark=triangle] table[x index = 0, y index={4}] {\tableinit};
          \addlegendentry{init GMG transfer};
          \addplot[gnuplot@purple,mark=diamond] table[x index = 0, y index={5}] {\tableinit};
          \addlegendentry{init smoother};
          \addplot[black,mark=x] table[x index = 0, y index={6}] {\tableinit};
          \addlegendentry{GMG V-cycle};
    \end{loglogaxis}
  \end{tikzpicture}
  \\
  \strut\hfill\pgfplotslegendfromname{legend:init}\hfill\strut
  \caption{Comparison of initialization costs of various data structures in the 9.1 release (left) and the new 9.2 release (right).}
  \label{fig:init_costs}
\end{figure}
